IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-04-26 main.tex
:pencil: Update manuscript

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly constrained by the received Radio-Frequency (RF) signal strength. To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency. This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously to a single-antenna User Equipment (UE) under the assist of an IRS. Considering energy harvester nonlinearity and practical receiving modes, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT). This non-convex problem is solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is retrieved by the Geometric Programming (GP) technique. Since the computational complexity of the GP algorithm scales exponentially with the number of carriers, we also propose two closed-form adaptive waveform schemes to facilitate practical SWIPT implementation. Simulation results demonstrate that the proposed algorithms bring considerable R-E gains and are robust to CSIT inaccuracy and finite IRS reflection states. Results also emphasize the importance of accounting harvester nonlinearity in the passive beamforming and entire IRS-aided SWIPT design.
	\end{abstract}

@@

	\begin{section}{Introduction}
		\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
			\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks has come to energy supply. Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic waves in the Radio-Frequency (RF) band. It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks. The upsurge in wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.

@@

		\begin{subsection}{Intelligent Reflecting Surface}
			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency. In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal for a smart reflection (i.e., passive beamforming). Different from the relay, backscatter, and Frequency-Selective Surface (FSS) \cite{Anwar2018}, the IRS adaptively assists the primary transmission with passive components to suppress thermal noise but is limited to frequency-dependent reflection.

@@

		\begin{subsection}{IRS-Aided SWIPT}
			Both SWIPT and IRS aim to achieve spectrum- and energy-efficient transmission, and the smart channel control and low power consumption of IRS are expected to bring more opportunities to SWIPT. For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}. It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links could boost the WSP because rank-deficient channels tend to require fewer energy beams. However, \cite{Wu2020b,Tang2019,Wu2020a} only consider single-carrier transmission based on an inaccurate linear energy harvester model. Unfortunately, such modeling is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}. In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS. We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.

			\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design. To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS modes. The proposed joint waveform, active and passive beamforming architecture exploits rectifier nonlinearity, beamforming gain, and channel selectivity across spatial and frequency domains to enlarge the achievable R-E region. This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT. By doing so, it is also the first paper to properly model the harvester nonlinearity (including its impact on both power and shape of the incoming waveform) and account for its crucial role in IRS-aided SWIPT.

			\emph{Second}, we characterize the achievable R-E region with multiple energy maximization problems with different rate constraints and solve each boundary point by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT). For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) under rectifier nonlinearity. For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and obtain the IRS phase shift by eigen decomposition with optimality proof. Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique. The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence. This is the first paper to jointly optimize waveform and active/passive beamforming in IRS-aided SWIPT.

			\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm. The Water-Filling (WF) strategy for modulated waveform and SMF strategy for multisine waveform are combined under TS and PS setups to facilitate practical SWIPT implementation. To accommodate the low-complexity waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio for TS and the combining and splitting ratios for PS. The proposed low-complexity designs achieve near-optimal R-E performance under different configurations.

@@

			\emph{Organization:} Section~\ref{se:system_model} introduces the system model, receiving modes, rectifier nonlinearity and R-E tradeoff. Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming optimization. Section~\ref{se:performance_evaluation} evaluates the proposed algorithms by simulation results. Section~\ref{se:conclusion_and_future_works} concludes the paper.

			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters. $j$ denotes the imaginary unit. $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix. $\boldsymbol{I}$ denotes the identity matrix. $\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denotes the subspace spanned respectively by real and complex $x \times y$ matrices. $\Re\{\cdot\}$ and $\Im\{\cdot\}$ denote respectively the real and imaginary part of a complex entity. $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm. $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector that retrieves the main diagonal of the input matrix. $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite. $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal. $\mathbb{E}_X\{\cdot\}$ takes expectation with respect to random variable $X$ ($X$ is omitted for simplicity). The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$. $\sim$ means ``distributed as''. $(\cdot)^{\star}$ and $(\cdot)^{(i)}$ denote respectively the stationary value and the value at iteration $i$.
		\end{subsection}
	\end{section}

@@

		\begin{subsection}{Reflection Pattern and Composite Channel}
			According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component. The former is fixed for a given antenna and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances. IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and its reflection coefficient is defined as
			\begin{equation}
				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l}
			\end{equation}
			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$. This paper sticks to the most common and simplest IRS model where the reflection amplitude is always assumed equal to \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift. We also define $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and let $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ be the IRS vector\footnote{Note the conjugate transpose in the notation of $\boldsymbol{\phi}$ makes its entries the complex conjugate of the diagonal entries of $\boldsymbol{\Theta}$.}.

@@

			\begin{remark}\label{re:subband_tradeoff}
				The cascaded channel response varies at different frequencies. Since we assume the reflection coefficient to be frequency-flat, there exists a tradeoff for auxiliary link control in the frequency domain. Moreover, each IRS element simultaneously assists all transmit antennas such that each reflection coefficient is shared by $M$ cascaded channels over $N$ subbands.
			\end{remark}
		\end{subsection}

		\begin{subsection}{Received Signal}
			The total received signal at the single-antenna UE can be decomposed as $y(t) \triangleq y_{\mathrm{I}}(t)+y_\mathrm{P}(t)$, where
			\begin{align}
				y_{\mathrm{I}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\},\label{eq:y_I}\\
				y_{\mathrm{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\mathrm{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}\label{eq:y_P}
			\end{align}
			capture the contribution of modulated and multisine waveforms over all subbands. Note that $y_{\mathrm{I}}(t)$ can also be used for energy harvesting if necessary, but $y_{\mathrm{P}}(t)$ is unmodulated and cannot be used for information decoding.
		\end{subsection}

@@

			As illustrated in Fig.~\ref{fi:receiver}, there are two practical schemes \cite{Zhou2013} for the co-located information decoder and energy harvester to utilize the superposed signal. The TS receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively. During each session, the transmitter optimizes the waveform for either Wireless Information Transfer (WIT) or WPT, while the receiver actives the information decoder or the energy harvester correspondingly. Varying $\eta$ from \num{0} to \num{1} characterizes a R-E segment from the WIT point to the WPT point. On the other hand, the PS receiver splits the incoming signal into individual data and energy streams with power ratio $1-\rho$ and $\rho$, respectively. The data stream is fed into the information decoder while the energy stream is fed into the energy harvester. During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different R-E tradeoff. In the following context, we focus on the analysis over the PS receiver because the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
		\end{subsection}

		\begin{subsection}{Information Decoder}
			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform. Therefore, the achievable rate writes as
			\begin{equation}\label{eq:R}
				R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)}
			\end{equation}
			where $\sigma_n^2$ is the variance of the total noise (at RF-band and during RF-to-baseband conversion) on tone $n$. Rate \eqref{eq:R} is achievable with either waveform cancellation or translated demodulation \cite{Clerckx2018b}.
		\end{subsection}

@@

			Rectifiers consist of nonlinear components like diode and capacitor to produce DC output and store energy \cite{Pinuela2013}. Consider a simplified rectifier model in Fig.~\ref{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load. As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function\footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
			\begin{equation}\label{eq:z}
				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}}
			\end{equation}
			where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage). With a slight abuse of notation, we refer to $z$ as the average output DC current in this paper. It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$. However, due to the coupling effect among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power. In other words, even-order terms with $i \ge 4$ account for the diode nonlinear behavior. For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}. Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which applies a modulation gain on the nonlinear terms of the output DC current. Inspired by \cite{Huang2017}, we further stack $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, and define $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$. As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}^{M \times M}$. Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4}.

@@

		Problem~\eqref{op:original} is intricate due to the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}. To obtain a feasible solution, we propose a suboptimal BCD algorithm that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.

@@

			Since $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices, $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real and we have

@@

			Therefore, the optimal active precoder is given by \eqref{eq:b_n} and no dedicated energy beam is required for the multisine component.
		\end{subsection}

>>>>

	\begin{abstract}
		The performance of Simultaneous Wireless Information and Power Transfer (SWIPT) is mainly constrained by the received Radio-Frequency (RF) signal strength. To tackle this problem, we introduce an Intelligent Reflecting Surface (IRS) to compensate the propagation loss and boost the transmission efficiency. This paper proposes a novel IRS-aided SWIPT system where a multi-carrier multi-antenna Access Point (AP) transmits information and power simultaneously, with the assist of an IRS, to a single-antenna User Equipment (UE) under practical receiving schemes. Considering energy harvester nonlinearity, we characterize the achievable Rate-Energy (R-E) region through a joint design of waveform, active and passive beamforming based on the Channel State Information at the Transmitter (CSIT). This non-convex problem is solved by the Block Coordinate Descent (BCD) method, where the active precoder is obtained in closed form, the passive beamformer is optimized by the Successive Convex Approximation (SCA) approach, and the waveform is retrieved by the Geometric Programming (GP) technique. Since the computational complexity of the GP algorithm scales exponentially with the number of carriers, we also propose two closed-form adaptive waveform schemes to facilitate practical SWIPT implementation. Simulation results demonstrate that the proposed algorithms bring considerable R-E gains and are robust to CSIT inaccuracy and finite IRS reflection states. Results also emphasize the importance of accounting harvester nonlinearity in the passive beamforming and entire IRS-aided SWIPT design.
	\end{abstract}

@@

	\begin{section}{Introduction}
		\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
			\IEEEPARstart{W}{ith} the great advance in communication performance, a bottleneck of wireless networks has come to energy supply. Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via Radio-Frequency (RF) waves. It provides low power at \si{\uW} level but broad coverage up to hundreds of meters in a sustainable and controllable manner, bringing more opportunities to the Internet of Things (IoT) and Machine to Machine (M2M) networks. The upsurge in wireless devices, together with the decrease of electronics power consumption, calls for a re-thinking of future wireless networks based on Wireless Power Transfer (WPT) and SWIPT \cite{Clerckx2019}.

@@

		\begin{subsection}{Intelligent Reflecting Surface}
			Intelligent Reflecting Surface (IRS) has recently emerged as a promising technique that adapts the propagation environment to enhance the spectrum and energy efficiency. In practice, an IRS consists of multiple individual sub-wavelength reflecting elements to adjust the amplitude and phase of the incoming signal for a smart reflection (i.e., passive beamforming). Different from the relay, backscatter and Frequency-Selective Surface (FSS) \cite{Anwar2018}, the IRS adaptively assists the primary transmission with passive components to suppress thermal noise but is limited to frequency-dependent reflection.

@@

		\begin{subsection}{IRS-Aided SWIPT}
			Both SWIPT and IRS aim to achieve spectrum- and energy-efficient transmission, and the smart channel control and low power consumption of IRS can bring more opportunities to SWIPT. For multi-user IRS-aided SWIPT systems, dedicated energy beams were proved unnecessary for the Weighted Sum-Power (WSP) maximization problem \cite{Wu2020b} but essential when fairness issue is considered \cite{Tang2019}. It was also demonstrated in \cite{Wu2020a} that Line-of-Sight (LoS) links could boost the WSP because rank-deficient channels tend to require fewer energy beams. However, \cite{Wu2020b,Tang2019,Wu2020a} only consider single-carrier transmission based on an inaccurate linear energy harvester model. Unfortunately, such modeling is known in both the RF and the communication literature to be inefficient and inaccurate \cite{Clerckx2019,Trotter2009,Clerckx2018,Clerckx2016a,Kim2019,Kim2020a,Kim2021,Clerckx2017,Kim2017,Clerckx2018b,Varasteh2020,Varasteh2019d,Varasteh2020a}. In this paper, we instead build our design based on a proper nonlinear harvester modeling that captures the dependency of the output DC power on both the power and shape of the input waveform, and marry the benefits of joint multi-carrier waveform and active beamforming optimization for SWIPT with the passive beamforming capability of IRS. We ask ourselves the important question: \emph{How to jointly exploit the spatial domain and the frequency domain efficiently through joint waveform and beamforming design to enlarge the R-E region of IRS-aided SWIPT?} The contributions of this paper are summarized as follows.

			\emph{First}, we propose a novel IRS-aided SWIPT architecture based on joint waveform, active and passive beamforming design. To make an efficient use of the rectifier nonlinearity, we superpose a multi-carrier unmodulated power waveform (deterministic multisine) to a multi-carrier modulated information waveform and evaluate the performance under TS and PS receiving modes. The proposed joint waveform, active and passive beamforming architecture exploits rectifier nonlinearity, beamforming gain, and channel selectivity across spatial and frequency domains to enlarge the achievable R-E region. This is the first paper to propose a joint waveform, active and passive beamforming architecture for IRS-aided SWIPT. By doing so, it is also the first paper to properly model the harvester nonlinearity (including its impact on both power and shape of the incoming waveform) and account for its crucial role in IRS-aided SWIPT.

			\emph{Second}, we characterize each R-E boundary point by energy maximization under rate constraint, and solve the problem by a Block Coordinate Descent (BCD) algorithm based on the Channel State Information at the Transmitter (CSIT). For active beamforming, we prove that the global optimal active information and power precoders coincide at Maximum-Ratio Transmission (MRT) even with rectifier nonlinearity. For passive beamforming, we propose a Successive Convex Approximation (SCA) algorithm and retrieve the IRS phase shift by eigen decomposition with optimality proof. Finally, the superposed waveform is optimized by the Geometric Programming (GP) technique. The IRS phase shift, active precoder, and waveform amplitude are updated iteratively until convergence. This is the first paper to jointly optimize waveform and active/passive beamforming in IRS-aided SWIPT.

			\emph{Third}, we introduce two closed-form adaptive waveform schemes to avoid the exponential complexity of the GP algorithm. The Water-Filling (WF) strategy for modulated waveform and the SMF strategy for multisine waveform are combined in the time domain and power domain to facilitate practical SWIPT implementation. To accommodate the suboptimal waveform schemes, we modify the passive beamforming algorithm and characterize the R-E region by varying the duration ratio under TS mode and the combining and splitting ratios under PS mode. The proposed low-complexity designs achieve near-optimal R-E performance in different scenarios.

@@

			\emph{Organization:} Section~\ref{se:system_model} introduces the system model. Section~\ref{se:problem_formulation} formulates the problem and tackles the waveform, active and passive beamforming design. Section~\ref{se:performance_evaluation} provides simulation results. Section~\ref{se:conclusion_and_future_works} concludes the paper.

			\emph{Notations:} Scalars, vectors and matrices are denoted respectively by italic, bold lower-case, and bold upper-case letters. $j$ denotes the imaginary unit. $\boldsymbol{0}$ and $\boldsymbol{1}$ denote respectively zero and one vector or matrix. $\boldsymbol{I}$ denotes the identity matrix. $\mathbb{R}^{x \times y}$ and $\mathbb{C}^{x \times y}$ denote respectively the subspace spanned by real and complex $x \times y$ matrices. $\Re\{\cdot\}$ and $\Im\{\cdot\}$ denote respectively the real and imaginary part of a complex entity. $(\cdot)^*$, $(\cdot)^T$, $(\cdot)^H$, $(\cdot)^+$, $\lvert{\cdot}\rvert$, $\lVert{\cdot}\rVert$ represent respectively the conjugate, transpose, conjugate transpose, ramp function, absolute value, and Euclidean norm. $\arg(\cdot)$, $\mathrm{rank}(\cdot)$, $\mathrm{tr}(\cdot)$, $\mathrm{diag}(\cdot)$ and $\mathrm{diag}^{-1}(\cdot)$ denote respectively the argument, rank, trace, a square matrix with input vector on the main diagonal, and a vector retrieving the main diagonal of the input matrix. $\boldsymbol{S} \succeq \boldsymbol{0}$ means $\boldsymbol{S}$ is positive semi-definite. $\mathbb{A}\{\cdot\}$ extracts the DC component of a signal. $\mathbb{E}_X\{\cdot\}$ takes expectation w.r.t. random variable $X$ ($X$ is omitted for simplicity). The distribution of a CSCG random vector with mean $\boldsymbol{0}$ and covariance $\boldsymbol{\Sigma}$ is denoted by $\mathcal{CN}(\boldsymbol{0},\boldsymbol{\Sigma})$. $\sim$ means ``distributed as''. $(\cdot)^{(i)}$ and $(\cdot)^{\star}$ denote respectively the $i$-th iterate and the stationary solution.
		\end{subsection}
	\end{section}

@@

		\begin{subsection}{Reflection Pattern and Composite Channel}
			According to Green's decomposition \cite{Hansen1989}, the backscattered signal of an antenna can be decomposed into the \emph{structural mode} component and the \emph{antenna mode} component. The former is fixed and can be regarded as part of the environment multipath, while the latter is adjustable and depends on the mismatch of the antenna and load impedances. IRS element $l \in \{1, \dots, L\}$ varies its impedance $Z_l = R_l + j X_l$ to reflect the incoming signal, and its reflection coefficient is defined as
			\begin{equation}
				\phi_l = \frac{Z_l - Z_0}{Z_l + Z_0} \triangleq \eta_l e^{j\theta_l}
			\end{equation}
			where $Z_0$ is the characteristic impedance, $\eta_l \in [0, 1]$ is the reflection amplitude\footnote{Due to the non-zero power consumption at the IRS, practically $R_l > 0$ such that $\eta_l < 1$ and is a function of $\theta_l$. This paper sticks to the most common IRS model where the reflection amplitude equals \num{1} so as to reduce the design complexity and provide a primary benchmark for practical IRS-aided SWIPT.}, and $\theta_l \in [0,2\pi)$ is the phase shift. We also define $\boldsymbol{\Theta} \triangleq \mathrm{diag}(\phi_1, \dots, \phi_L) \in \mathbb{C}^{L \times L}$ as the IRS matrix and let $\boldsymbol{\phi} \triangleq [\phi_1, \dots, \phi_L]^H \in \mathbb{C}^{L \times 1}$ be the IRS vector\footnote{Note that $\boldsymbol{\phi}=\mathrm{diag}(\boldsymbol{\Phi}^*)$ by definition.}.

@@

			\begin{remark}\label{re:subband_tradeoff}
				The cascaded channel varies at different frequencies. Since we regard the reflection as frequency-flat, there exists a tradeoff for auxiliary link control in the frequency domain. Moreover, the IRS simultaneously assists all transmit antennas such that each reflection coefficient is shared by $M$ auxiliary links over $N$ subbands.
			\end{remark}
		\end{subsection}

		\begin{subsection}{Received Signal}
			The total received signal at the single-antenna UE can be decomposed as $y(t) \triangleq y_{\mathrm{I}}(t)+y_\mathrm{P}(t)$, where
			\begin{align}
				y_{\mathrm{I}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}{\boldsymbol{w}_{\mathrm{I},n}\tilde{x}_{\mathrm{I},n}(t)}{e^{j2{\pi}{f_n}{t}}}\right\},\label{eq:y_I}\\
				y_{\mathrm{P}}(t) & = \Re\left\{\sum_{n=1}^N{\boldsymbol{h}_{n}^H}\boldsymbol{w}_{\mathrm{P},n}{e^{j2{\pi}{f_n}{t}}}\right\}\label{eq:y_P}
			\end{align}
			capture respectively the modulated and multisine components. Note that $y_{\mathrm{I}}(t)$ can also be used for energy harvesting, but $y_{\mathrm{P}}(t)$ is unmodulated and cannot be used for information decoding.
		\end{subsection}

@@

			As illustrated in Fig.~\ref{fi:receiver}, there are two practical schemes for the co-located information decoder and energy harvester \cite{Zhou2013} to utilize the superposed signal. The TS receiver divides each transmission block into orthogonal data and energy sessions with duration $1-\eta$ and $\eta$, respectively. During each session, the transmitter optimizes the waveform for either Wireless Information Transfer (WIT) or WPT, while the receiver activates the information decoder or the energy harvester correspondingly. Varying $\eta$ from \num{0} to \num{1} characterizes a R-E segment from the WIT point to the WPT point. On the other hand, the PS receiver splits the incoming signal into individual data and energy streams with power ratio $1-\rho$ and $\rho$, respectively. The data stream is fed into the information decoder while the energy stream is fed into the energy harvester. During each transmission block, the superposed waveform and splitting ratio are jointly designed to achieve different R-E tradeoff. In the following context, we focus on the analysis over the PS receiver since the TS receiver can be regarded as a special case (i.e., a time sharing between $\rho=0$ and $\rho=1$).
		\end{subsection}

		\begin{subsection}{Information Decoder}
			A major benefit of the superposed waveform is that the multisine is deterministic and creates no interference to the modulated waveform. Therefore, the achievable rate writes as
			\begin{equation}\label{eq:R}
				R(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\rho) = \sum_{n=1}^N{\log_2\left(1+\frac{(1-\rho)\lvert \boldsymbol{h}_{n}^H\boldsymbol{w}_{\mathrm{I},n} \rvert^2}{\sigma_n^2}\right)}
			\end{equation}
			where $\sigma_n^2$ is the variance of the noise at RF-band and during RF-to-baseband conversion on tone $n$. Rate \eqref{eq:R} is achievable with waveform cancellation or translated demodulation \cite{Clerckx2018b}.
		\end{subsection}

@@

			Rectifiers consist of nonlinear components like diode and capacitor to produce DC output and store energy \cite{Pinuela2013}. Consider a simplified rectifier model in Fig.~\ref{fi:single_diode_rectifier} where a single series diode is followed by a low-pass filter with a parallel load. As detailed in \cite{Clerckx2016a}, a truncated Taylor expansion of the diode I-V characteristic equation suggests that, when the subband frequencies are evenly-spaced, maximizing the average output DC current is equivalent to maximizing a monotonic function\footnote{Note that this small-signal expansion model is only valid for the nonlinear operation region of the diode, and the I-V relationship would be linear if the diode behavior is dominated by the load \cite{Clerckx2016a}.}
			\begin{equation}\label{eq:z}
				z(\boldsymbol{\phi},\boldsymbol{w}_{\mathrm{I}},\boldsymbol{w}_{\mathrm{P}},\rho)=\sum_{i\,\mathrm{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\mathrm{A}}^{i/2}}{\mathbb{E}\left\{\mathbb{A}\left\{y(t)^i\right\}\right\}}
			\end{equation}
			where $n_0$ is the truncation order and $k_i \triangleq i_{\mathrm{S}}/i!(n'v_{\mathrm{T}})^i$ is the diode coefficient ($i_{\mathrm{S}}$ is the reverse bias saturation current, $n'$ is the diode ideality factor, $v_{\mathrm{T}}$ is the thermal voltage). With a slight abuse of notation, we refer to $z$ as the average output DC current in this paper. It can be observed that the traditional linear harvester model, where the output DC power equals the sum of the power harvested on each frequency, is a special case of \eqref{eq:z} with $n_0=2$. However, due to the coupling effect among different frequencies, some high-order AC components compensate each other and further contribute to the output DC power. In other words, even-order terms with $i \ge 4$ account for the diode nonlinear behavior. For simplicity, we choose $n_0=4$ to investigate the fundamental rectifier nonlinearity, and define $\beta_2 \triangleq {k_2}{R_{\mathrm{A}}}$, $\beta_4 \triangleq {k_4}{R_{\mathrm{A}}^2}$ to rewrite $z$ by \eqref{eq:z_expand}. Note that $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^2\right\}=1$ but $\mathbb{E}\left\{\lvert\tilde{x}_{\mathrm{I},n}\rvert^4\right\}=2$, which applies a modulation gain on the nonlinear terms of the output DC current. Inspired by \cite{Huang2017}, we further stack $\boldsymbol{h} \triangleq [\boldsymbol{h}_1^T,\dots,\boldsymbol{h}_N^T]^T \in \mathbb{C}^{MN \times 1}$, $\boldsymbol{w}_{\mathrm{I/P}} \triangleq [\boldsymbol{w}_{\mathrm{I/P},1}^T,\dots,\boldsymbol{w}_{\mathrm{I/P},N}^T]^T \in \mathbb{C}^{MN \times 1}$, and define $\boldsymbol{W}_{\mathrm{I/P}} \triangleq \boldsymbol{w}_{\mathrm{I/P}}\boldsymbol{w}_{\mathrm{I/P}}^H \in \mathbb{C}^{MN \times MN}$. As illustrated by Fig.~\ref{fi:block_diagonal}, $\boldsymbol{W}_{\mathrm{I/P}}$ can be divided into $N \times N$ blocks of size $M \times M$, and we let $\boldsymbol{W}_{\mathrm{I/P},k}$ keep its block diagonal $k \in \{-N+1,\dots,N-1\}$ and set all other blocks to $\boldsymbol{0}$. Hence, the components of $z$ reduce to \eqref{eq:y_I2}--\eqref{eq:y_P4}.

@@

		Problem~\eqref{op:original} is intricate due to the coupled variables in \eqref{ob:original}, \eqref{co:original_rate} and the non-convex constraint \eqref{co:original_modulus}. To obtain a feasible solution, we propose two BCD algorithms that iteratively updates 1) the IRS phase shift, 2) the active precoder, 3) the waveform amplitude and splitting ratio, until convergence.

@@

			Since $\boldsymbol{C}_{\mathrm{I/P},0}$ and $\boldsymbol{\Phi}$ are Hermitian matrices, $t_{\mathrm{I/P},0}=\mathrm{tr}(\boldsymbol{C}_{\mathrm{I/P},0}\boldsymbol{\Phi})$ is real. Due to symmetry, we have

@@

			% Therefore, the optimal active precoder is given by \eqref{eq:b_n} and no dedicated energy beam is required for the multisine component.
		\end{subsection}
